Titeln på avhandlingens språk

### 2023-05-08 publications/2023EdgeDroid2/resources/glossary.tex

\usepackage{glossaries}%! suppress = MissingImport
\newacronym[longplural={Wearable Cognitive Assistants}]{WCA}{WCA}{Wearable Cognitive Assistance}
\newacronym[longplural={Augmented Realities}]{AR}{AR}{Augmented Reality}
\newacronym[longplural={Virtual Realities}]{VR}{VR}{Virtual Reality}
\newacronym[longplural={eXtended Realities}]{XR}{XR}{eXtended Reality}
\newacronym{GPU}{GPU}{Graphical Processing Unit}
\newacronym{FPS}{FPS}{Frames Per Second}
\newacronym{DNN}{DNN}{Deep Neural Network}
\newacronym{CPS}{CPS}{Cyber-Physical System}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{NCS}{NCS}{Networked Control System}
%\acroindefinite{NCS}{an}{a}

@@

>>>>

%! suppress = MissingImport
\newacronym[longplural={Wearable Cognitive Assistants}]{WCA}{WCA}{Wearable Cognitive Assistance}
\newacronym[longplural={Augmented Realities}]{AR}{AR}{Augmented Reality}
\newacronym[longplural={Virtual Realities}]{VR}{VR}{Virtual Reality}
\newacronym[longplural={eXtended Realities}]{XR}{XR}{eXtended Reality}
\newacronym[longplural={Mixed Realities}]{MR}{MR}{Mixed Reality}
\newacronym{MAR}{MAR}{Mobile \nestedgls{AR}}
\newacronym{GPU}{GPU}{Graphical Processing Unit}
\newacronym{FPS}{FPS}{Frames Per Second}
\newacronym{DNN}{DNN}{Deep Neural Network}
\newacronym{CPS}{CPS}{Cyber-Physical System}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{NCS}{NCS}{Networked Control System}

@@

\newacronym{2D}{2-D}{two-dimensional}
\newacronym{3D}{3-D}{three-dimensional}
\newacronym{PD}{PD}{Proportional-Differential}
\newacronym{PID}{PID}{Proportional-Integral-Differential}
\newacronym{SDK}{SDK}{Software Development Kit}
\newacronym{YCSB}{YCSB}{Yahoo! Cloud Serving Benchmark}
\newacronym{ITS}{ITS}{Intelligent Transportation System}
\newacronym{OOS}{OoS}{Out-of-Scope}
\newacronym{OMNET}{OMNeT++}{Objective Modular Network Testbed in C++}
\newacronym{ns2}{ns-2}{network simulator 2}
\newacronym{ns3}{ns-3}{network simulator 3}
\newacronym{IRB}{IRB}{Institutional Review Board}
\newacronym{IaaS}{IaaS}{Infrastructure-as-a-Service}
\newacronym{CC}{CC}{Creative Commons}
\newacronym{CCBY}{CCBY}{\nestedgls{CC} Attribution 2.0 Generic~\cite{ccbylicense}}
\newacronym{CC0}{CC0}{\nestedgls{CC} Zero 1.0 Universal Public Domain Dedication~\cite{cczerolicense}}
